Appendix A: Stochastic simulations of noisy phenomena

### 2017-10-27 appendixA/appendixA.Rmd
tweaking graphs

## plot themes, non-essential
library(hrbrthemes)
library(ggthemes)
ggplot2::theme_set(hrbrthemes::theme_ipsum())
colours <- ptol_pal()(2)

@@

```{r}
p <- list(r = .5, K = 2, Q = 5, H = .38, sigma = .04, a = 0.245, N = 1e4)
f <- function(x) x * p$r * (1 - x / p$K)
g <- function(x) p$a * x ^ p$Q / (x^p$Q + p$H^p$Q)
x <- seq(0,2, length.out = 100)

p2 <- data.frame(x, f = f(x), g = g(x)) %>%
  ggplot(aes(x, y)) + 
  geom_line(aes(y = f), col=colours[1], lwd=1) +
  geom_line(aes(y = g), col=colours[2], lwd=1) + labs(x = bquote(X[t]), y = bquote(X[t+1]))

@@

p1 <- tipping %>%
  select(-x) %>%
  gather(series, value, -t, -tip_time) %>%
  ggplot(aes(t, value)) + geom_line() + 
  geom_vline(aes(xintercept = tip_time), col="red", lty=2) +
  facet_wrap(~series, ncol = 2, scales="free_y") + theme_ipsum() + 
  labs(title="A: Early warning signs")

p2 <- tipping %>% 
  select(t, population = x, tip_time) %>%
  ggplot(aes(t, population)) + geom_line() + 
  geom_vline(aes(xintercept = tip_time), col="red", lty=2) + 
  scale_y_log10() + 
  theme_ipsum()+ labs(title="B: Population density",
                      caption = "Vertical red dashed line indicates tipping point location")

>>>>

## plot themes, non-essential
library(ggthemes)
library(gridExtra)
#library(hrbrthemes)
#ggplot2::theme_set(hrbrthemes::theme_ipsum())
ggplot2::theme_set(theme_bw())
colours <- ptol_pal()(2)

@@

p <- list(r = .5, K = 2, Q = 5, H = .38, sigma = .04, a = 0.245, N = 1e4)
f <- function(x) x * p$r * (1 - x / p$K)
g <- function(x) p$a * x ^ p$Q / (x^p$Q + p$H^p$Q)
x <- seq(0,2, length.out = 100)

data.frame(x, growth = f(x), consumption = g(x)) %>%
  gather(curve, y, -x) %>%
  ggplot(aes(x, y, col=curve)) +
  geom_line(lwd=1) + 
  scale_color_ptol() + 
  labs(x = bquote(X[t]), y = bquote(X[t+1]), subtitle= bquote(bold(B.)))
```

@@

p1 <- tipping %>%
  select(-x) %>%
  gather(series, value, -t, -tip_time) %>%
  ggplot(aes(t, value)) + geom_line() + 
  geom_vline(aes(xintercept = tip_time), col="red", lty=2) +
  facet_wrap(~series, ncol = 2, scales="free_y") +
  #theme_ipsum() + 
  labs(title="A: Early warning signs")

p2 <- tipping %>% 
  select(t, population = x, tip_time) %>%
  ggplot(aes(t, population)) + geom_line() + 
  geom_vline(aes(xintercept = tip_time), col="red", lty=2) + 
  scale_y_log10() + 
#  theme_ipsum() + 
  labs(title="B: Population density",
              caption = "Vertical red dashed line indicates tipping point location")
